Analysis only with the first instance

### 2022-09-16 analysis/firstInstance.Rmd
add analysis only with the first instance
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Primary analysis'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of primary analysis.

@@

@@

```{r ioi}
# for each individual
ioi_trial <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2)]

@@

```{r kot, echo = FALSE}
# for each individual
kot_trial <- dt_kot[Articulation == "Legato" | Articulation == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Articulation)]

@@

```{r vel, echo = FALSE}
# for each individual
vel_trial <- dt_vel[Dynamics != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Dynamics)]

@@

```{r vel-diff, echo = FALSE}
# for each individual
vel_diff_trial <- dt_vel_diff[Dynamics == "FtoP" | Dynamics == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Dynamics)]

>>>>

---
title: 'Analysis only with the first instance'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of analysis which only include the performance with the first instance of each student (category).

@@

```{r, include = FALSE}
info <- dt_ioi[, .(N = .N), by = .(SubNr, TrialNr, Stimuli, Category)]
info

dt_ioi_first <- data.table()
for (subnr in unique(info$SubNr)){
  for (category in unique(info[SubNr == subnr]$Category)){
    trials <- unique(info[SubNr == subnr & Category == category]$TrialNr)
    current <- dt_ioi[SubNr == subnr & Category == category & TrialNr == min(trials)]
    dt_ioi_first <- rbind(dt_ioi_first, current)
  }
}

dt_kot_first <- data.table()
for (subnr in unique(info$SubNr)){
  for (category in unique(info[SubNr == subnr]$Category)){
    trials <- unique(info[SubNr == subnr & Category == category]$TrialNr)
    current <- dt_kot[SubNr == subnr & Category == category & TrialNr == min(trials)]
    dt_kot_first <- rbind(dt_kot_first, current)
  }
}

dt_vel_first <- data.table()
for (subnr in unique(info$SubNr)){
  for (category in unique(info[SubNr == subnr]$Category)){
    trials <- unique(info[SubNr == subnr & Category == category]$TrialNr)
    current <- dt_vel[SubNr == subnr & Category == category & TrialNr == min(trials)]
    dt_vel_first <- rbind(dt_vel_first, current)
  }
}

dt_vel_diff_first <- data.table()
for (subnr in unique(info$SubNr)){
  for (category in unique(info[SubNr == subnr]$Category)){
    trials <- unique(info[SubNr == subnr & Category == category]$TrialNr)
    current <- dt_vel_diff[SubNr == subnr & Category == category & TrialNr == min(trials)]
    dt_vel_diff_first <- rbind(dt_vel_diff_first, current)
  }
}
```

@@

```{r ioi}
# for each individual
ioi_trial <- dt_ioi_first[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2)]

@@

```{r kot, echo = FALSE}
# for each individual
kot_trial <- dt_kot_first[Articulation == "Legato" | Articulation == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Articulation)]

@@

```{r vel, echo = FALSE}
# for each individual
vel_trial <- dt_vel_first[Dynamics != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Dynamics)]

@@

```{r vel-diff, echo = FALSE}
# for each individual
vel_diff_trial <- dt_vel_diff_first[Dynamics == "FtoP" | Dynamics == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation2, Dynamics2, Dynamics)]
